Data Processing

### 2019-11-29 analysis/data_processing.Rmd
add heatmap

library(tidyverse)
library(knitr)
library(langcog)
library(ggthemes)
library(jsonlite)
library(readxl)
library(corrr)
library(corrplot)

@@

data <- raw_data %>%
  filter(trial != "training", 
         trial != "filler1", 
         trial != "filler2",
         trial != "train",
         trial != "train2")%>%
  filter(phase == "shape" | is.na(phase))%>%
  select(subid, subage, test_date, task, trial, correct)%>%
  separate(subid, into = c("id","test_day"), sep="\\.")

raw_data %>%
  filter(
         trial == "filler1" | 
         trial == "filler2")

@@

```{r}
data%>%
  group_by(task)%>%
  summarise(n= length(unique(id)))
```

@@

>>>>

library(tidyverse)
library(knitr)
library(langcog)
library(ggthemes)
library(jsonlite)
library(readxl)
library(corrr)
library(corrplot)
library(ggcorrplot)
library(reshape2)

@@

unique(raw_data$subid)

data <- raw_data %>%
  filter(trial != "training", 
         trial != "filler1", 
         trial != "filler2",
         trial != "train",
         trial != "train2")%>%
  filter(phase == "shape" | is.na(phase))%>%
  mutate(subid = recode(subid, `13.2` = "Vp13.2",
                        `13.2` = "Vp13.2",
                        `14.2` = "Vp14.2",
                        `16.2` = "Vp16.2",
                        `19.1` = "Vp19.1",
                        `12.1` = "Vp12.1"
                        ))%>%
  select(subid, subage, test_date, task, trial, correct)%>%
  separate(subid, into = c("id","test_day"), sep="\\.")%>%
  mutate(test_day = ifelse(id == "Vp12" & test_date =="2019-11-26", 2, test_day))

data %>%
  group_by(id, test_day, test_date)%>%
  summarise(n())%>%
  arrange(id,test_date)

@@

```{r}
data%>%
  group_by(subage)%>%
  summarise(n= length(unique(id)))
```

```{r}
data%>%
  group_by(test_day,task)%>%
  summarise(n= length(unique(id)))
```

@@

```{r}
p3 <- data%>%
  filter(task != "training")%>%
  group_by(id,task, test_day)%>%
  summarise(mean = mean(correct))%>%
  spread(test_day, mean)%>%
  rename("Day1" = `1`,
         "Day2" = `2`)%>%
  na.omit()

ggplot(p3, aes(x = Day1, y = Day2))+
  geom_jitter(width = .05, height = .05, alpha = .5)+
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 0.7, size = 0.5)+
  geom_smooth(method = "lm", col = "#af6300")+
  facet_grid(~task)+
  coord_fixed()+
  xlim(-.1,1.1)+
  ylim(-.1,1.1)+
  theme_few()

```{r}
reli <- data%>%
  filter(task != "training")%>%
  group_by(id,task, test_day)%>%
  summarise(mean = mean(correct))%>%
  spread(test_day, mean)%>%
  na.omit()%>%
  rename("Day1" = `1`,
         "Day2" = `2`)%>%
  group_by(task)%>%
  summarize(reli = cor.test(Day1,Day2)$estimate,
            lci = cor.test(Day1,Day2)$conf.int[1],
            uci = cor.test(Day1,Day2)$conf.int[2],
            p = cor.test(Day1,Day2)$p.value)%>%
  mutate_if(is.numeric, round, digits = 2)

reli
```

```{r}
cor <- data%>%
  filter(task != "training")%>%
  group_by(id,task)%>%
  summarise(mean = mean(correct))%>%
  spread(task, mean)%>%
  ungroup()%>%
  select(-id)%>%
  corrr::correlate(diagonal = reli$reli)%>%
  gather(task, cor, -rowname)%>%
  mutate_if(is.numeric, round, digits = 2)%>%
  mutate(cor = replace(cor, duplicated(cor), NA))%>%
  na.omit()

ggplot(cor, aes(x = rowname, y = task, fill = cor))+
  geom_tile(color = "white")+
  labs(x = "", y = "")+
  scale_fill_gradient2(low = "#CC6677", high = "#117733", mid = "white", 
   midpoint = 0, limit = c(-1,1), space = "Lab", 
   name="Correlation") +
   coord_fixed()+
  theme_few(base_size = 12)+
  geom_text(aes(label = cor), color = "black", size = 3) +
  theme(legend.justification = c(1, 0),
        legend.position = c(0.55, 0.7),
        legend.direction = "horizontal",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))+
  guides(fill = guide_colorbar(barwidth = 7, barheight = 1,
                title.position = "top", title.hjust = 0.5))
```
